Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-07-13 Journal1/Response3/Response.tex

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TNSM \\[-6ex]}
\date{}

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their constructive comments on our manuscript. They have been beneficial in revising this paper, and we have improved the technical content and presentation quality through their assistance. We greatly appreciate their generous help. In addition, we would like to acknowledge the assistance of Dr. Onel Luis Alcaraz López in this revision.
Moreover, we have reviewed and incorporated all the comments and suggestions.
Additionally, we removed two figures of Fig. 2 and Fig. 3 since they don't add much to what is already written in words after revision. Even after this revision (comment 2 of reviewer 3), Fig. 2 makes the paper vaguer. We also aim for a more concise manuscript.
We hope that the modifications we have made to the manuscript and the responses we have provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

@@

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent  Comments to the Author} ``I think the paper should undergo a major revision. It is important to take special attention to the comments of reviewer 2.''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the Editor for his comments and for giving us this opportunity to improve our paper. We have used the comments to improve our paper and eliminate problems. We are confident that we were able to address the reviewers’ and editor’s suggestions.

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We apologize for not considering this comment correctly in the previous version.
Thank you for this comment. We moved the related works from sub-section to the section part and modified it as below.

@@

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
In [2], the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
In [18], a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services. Moreover, [19] investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
In  [5], the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

In [9], [20], the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
Paper [9] aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
In  [21], [22], the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.

In  [23],[24], the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
Finally, in [25], the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague. It is still not clear how this process is achieved and how it is linked to their method. I was expecting at least a connection or introduction to Fig.1 where the system is shown. Additionally, more information with respect to the interaction with the system would have been required in that regard. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for the given remark. We modified and clarified the description of the life cycle of a network slice. We report the relation between Fig. 1 and the network slice management and explain more about our algorithm in the related subsection below

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment7:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that. The authors’ response points to Fig. 11. However if one looks at Fig.11 carefully, understands that only the Aggregate throughput is shown there. Even if one considers the Section III-C1 and III-C2 that the authors demonstrate as their convergence analysis and proof, there is no evidence or clarification of any delay value with respect to their algorithm’s convergence. On the one hand it is very beneficial to have a mathematical proof that the algorithm converges. On the other hand, it is equally important to portray these findings with numerical values. In any case, this is not applicable in the current version of the manuscript. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We apologize for wrongly responding to this comment in the previous version of the response letter.
Based on this comment, we added Fig. 11 and Table III to our manuscript.
Below, we reported these changes.

In Fig. 11,  the mean total delay is indicated according to the number of iterations. In Table III, we reported the execution delay time according to the number of UEs in the system to investigate the full consideration of the reviewer.

In Fig. \ref{fig:2}, the mean total delay is indicated according to the number of iterations of the
proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.
\begin{figure}[H]
  \centering
    \includegraphics[scale = 0.5]{iterD.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Mean Total Delay (usec) vs. Number of iterations}
  \label{fig:2}
\end{figure}

Table III shows the execution delay time versus the number of UEs for one service. We run our simulation on the system with configures (RAM = 8 GB, CPU = Core i5, SSD Hard Disk). 
 As the number of UEs in the system increases, the execution time increases polynomially. 
Moreover, we added Fig. \ref{fig:3} to the response letter, which is equal to Table III, but for space reasons, we reported Table III instead of Fig. \ref{fig:3}.
\begin{figure}[H]
  \centering
    \includegraphics[scale = 0.5]{exec.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Execution Time vs. Number of UEs}
  \label{fig:3}
\end{figure}

\begin{table}[H]
\captionsetup{labelformat=empty}
 \caption {Table(III) Execution Time vs. Number of UEs} 
\begin{center}
 \scalebox{0.9}{
\begin{tabular}{|| l || l| l |l |l |l ||}
 \hline
Number of UEs & 5 & 10 & 15 & 20 & 25 \\ 
Execution Time (usec)& 12.156 & 19.156 &  29.140 & 44.573 & 67.912 \\
 \hline
\end{tabular}}
\end{center}
\end{table}

@@

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment8:} `As a final remark, the structure of the paper needs major re-construction. Several Sections are very lengthy and could be reduced while creating additional Sections. In the current format it is very hard to follow. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment to make our paper more readable. We modified the entire paper based on this comment.
We updated the manuscript while creating additional Sections such as "background" and "related literature" Sections. Moreover, we modified and shortened the unnecessary paragraphs, for instance, in the "introduction," "system model," and "numerical results." Our paper was modified totally to satisfy the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment9:} `Moreover, there are some typos in the manuscript. For instance, user equipements: user equipment.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We appreciate your comment about troubleshooting our paper and removing mistakes. Using this comment as a guide, we modified the entire paper. We revised semantic and grammar problems. We reread our paper and tried to correct mistakes the same as this.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment10:} `Furthermore, some acronyms are not explained in the text e.g., Quality of Service (QoS). ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Based on this comment, we added Table I reporting the list of acronyms to our paper as follows to relieve the reviewer's concern.

@@

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment11:} `Finally, the figures in the current version of the manuscript are very small and extremely hard to read. Therefore, re-formatting is necessary. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We modified all figures to make them more readable due to this comment. We enlarge the texts of the figures, bold the lines and markers, and re-formatting all the figures.

\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 3} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The reviewer has addressed most of the comments satisfactorily. However, the paper still contains some minor issues as follows ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We are pleased to thank the reviewer for his/her detailed and thorough reading of this manuscript. We hope that the responses provided here will assist the reviewer in relieving his or her concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``Abbreviations such as QoS, CAPEX and OPEX are not expanded at their first use. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Based on this comment, we added Table I reporting the list of acronyms to the paper shown below to address the reviewer's concern.

@@

   O-CU &  O-RAN central unit \\ [.5ex]

     UPF &  user plane function \\ [.5ex]

  UE &  user equipment \\ [.5ex]
  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
  CAPEX & capital expenditures  \\ [.5ex]
  OPEX & operating expenses  \\ [.5ex]

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} ``Eq. (3) includes inter-slice interference but a sentence following the equation mentions that there is no inter-slice interference because slices are isolated, which is confusing''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\} 
We thank the reviewer for reporting this ambiguity.
We revised this section and rewrote equation (3) by removing the inter-slice interference to clarify this equation. Moreover, we removed two figures of Fig. 2 and Fig. 3 since they don't add much to what is already written in words after revision, and even after this revision, Fig. 2 makes the paper vaguer. We also aim for a more concise manuscript.
Below we report the revised sentences.

### 2022-07-14 Journal1/paper5TNSM/pr.tex
add sth

The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services, remains as a key research problem.
In this paper, we study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.

@@

The optimization of baseband resources includes O-RAN radio unit (O-RU) and physical resource block (PRB) assignment, and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.

@@

The proposed method is validated via simulations which evince the achievement of a higher data rate and lower end-to-end delay than existing methods.

@@

\textcolor{MidnightBlue}{Network slicing techniques significantly reduce inter-service (inter-slice) interference.
One way consists in leveraging a two-time scale PRB scheduling to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale). Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}. In this paper, we assume that the PRB scheduling is performed. Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
Since there are limited resources, inter-service interference cannot be eliminated entirely. Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.}
%\begin{figure}
%  \centering
%  \captionsetup{justification=centering}
%    \includegraphics[scale = 0.35]{Interference.png}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Type of Interference Signal}
%  \label{fig:intf}
%\end{figure}

@@

 Herein, we consider a zero forcing beamforming vector, which minimizes the experienced interference, and is given by \cite{huang2013user}
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{k \: H} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}.
\end{equation}
\noindent where $\bold{h}_{r,u(s,i)}^{k}$ is the channel estimate, which is assumed imperfect. Mathematically,
$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$, where
$\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
\vspace*{-.8em}
\subsection{Achievable Data Rate}
The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as 
\begin{equation}\label{eq3}
\mathcal{R}_{u(s_1,i)} = \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
\end{equation}
where
\begin{equation}
\mathcal{R}_{r, u(s_1,i)} = \sum_{k=1}^{K} \mathcal{{R}}_{r,u(s_1,i)}^{k} e^k_{r,u(s_1,i)},
\end{equation}
is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
\begin{equation}
\mathcal{{R}}_{r,u(s_1,i)}^{k} =  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}),
\end{equation}
%\begin{subequations}\label{eq3}
%\begin{alignat}{4}
%\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
%\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
%\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
%\end{alignat}
%\end{subequations}
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the application of service type 2 (URLLC) and 3 (mMTC) is not achieved from the Shannon capacity formula. Instead, in a short packet transmission, the achievable data rate is approximated as \cite{setayesh2020joint}
\begin{equation}\label{eq11}
\mathcal{R}_{u(s_j,i)} = \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
\end{equation}
where
\begin{equation}
\mathcal{R}_{r,u(s_j,i)} = \mathcal{{R}}_{r,u(s_j,i)}^{k}{e}_{u(s_j,i)}^{k},
\end{equation}
is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
\begin{equation}
\mathcal{{R}}_{r,u(s_j,i)}^{k} = B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},
\end{equation}
%\begin{subequations}\label{eq11}
%\begin{alignat}{4}
%\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
%\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
%\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
%\end{alignat}
%\end{subequations}
where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
%{\color{red} check paranthesis. }
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}.
\end{equation}
%{\color{red} what is transmission probability? }
Here, $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of the Q function,
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$ and PRB $k$, while
$N_{u(s_j,i)}^{k}$ represents the corresponding transmit blocklength.
$\mathcal{R}_{r,u(s_j,i)}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

\begin{figure*}[!htb]
	\centerline{%
		\begin{tabular}{c@{}c@{}c}			
			\includegraphics[scale = 0.41]{fig/priorityLastn.eps} &
			\includegraphics[scale = 0.41]{fig/itern.eps} &
			\includegraphics[scale = 0.41]{fig/iterD.eps} \\
			\scriptsize Fig. 9~~Throughput of eMBB services vs. priority of the first one  & \scriptsize Fig. 10~~Aggregate throughput vs. number of iterations  & \scriptsize Fig. 11~~Mean Delay (usec) vs. number of iterations 
	\end{tabular}}
	%\caption{Global caption.}
	\label{label}
\end{figure*}

@@

\textcolor{MidnightBlue}{In Fig. 11, the mean total delay is indicated according to the number of iterations of the
proposed algorithm (IABV) for different numbers of UEs for one service. This figure shows that the algorithm converged to the fixed value after four iterations.}

>>>>

The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements while establishing priorities and promoting balance between the significantly heterogeneous services remains a key research problem.
In this paper, we use network slicing to study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems.

@@

Optimizing baseband resources includes O-RAN radio unit (O-RU), physical resource block (PRB) assignment, and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve.

@@

The proposed method is validated via simulations, which achieve a higher data rate and lower end-to-end delay than existing methods.

@@

\textcolor{MidnightBlue}{Network slicing techniques significantly reduce inter-service (inter-slice) interference.
One way to leverage a two-time scale PRB scheduling is to isolate PRBs in slices (in the first time scale) and schedule the PRBs to the UEs of the slices (in the second time scale). Another method consists of allocating part of the PRBs of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}. In this paper, we assume that the PRB scheduling is performed. Also, in Section \ref{prb}, we briefly study the PRB scheduling between slices.
Since there are limited resources, inter-service interference cannot be eliminated entirely. Nevertheless, isolating the slices reduces inter-service interference considerably and allows us to ignore it mathematically.}
%\begin{figure}
%  \centering
%  \captionsetup{justification=centering}
%    \includegraphics[scale = 0.35]{Interference.png}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Type of Interference Signal}
%  \label{fig:intf}
%\end{figure}

@@

 Herein, we consider a zero forcing beamforming vector, which minimizes the experienced intra-slice interference, and is given by \cite{huang2013user}
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = \hat{\bold{h}}_{r,u(s,i)}^{k}(\hat{\bold{h}}_{r,u(s,i)}^{k \: H} \hat{\bold{h}}_{r,u(s,i)}^{k})^{-1}.
\end{equation}
\noindent where $\bold{h}_{r,u(s,i)}^{k}$ is the channel estimate, which is assumed imperfect. Mathematically,
$\hat{\boldsymbol{h}}_{r,u(s,i)} = \boldsymbol{h}_{r,u(s,i)} + \Delta \boldsymbol{h}_{r,u(s,i)}$, where
$\Delta \boldsymbol{h}_{r,u(s,i)}\sim \mathcal{N}(0,\boldsymbol{\phi}_{r,u(s,i)}^2)$ indicates the estimating error vector with a Gaussian distribution and $\boldsymbol{\phi}_{r,u(s,i)} = \text{diag}(\phi_{r,u(s,i)},\ldots,\phi_{r,u(s,i)}).$
\vspace*{-.8em}
\subsection{Achievable Data Rate}
The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as 
\begin{equation}\label{eq3}
\mathcal{R}_{u(s_1,i)} = \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
\end{equation}
where
\begin{equation}
\mathcal{R}_{r, u(s_1,i)} = \sum_{k=1}^{K} \mathcal{{R}}_{r,u(s_1,i)}^{k} e^k_{r,u(s_1,i)},
\end{equation}
is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
\begin{equation}
\mathcal{{R}}_{r,u(s_1,i)}^{k} =  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}),
\end{equation}
%\begin{subequations}\label{eq3}
%\begin{alignat}{4}
%\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
%\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
%\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},
%\end{alignat}
%\end{subequations}
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the application of service type 2 (URLLC) and 3 (mMTC) is not achieved from the Shannon capacity formula. Instead, in a short packet transmission, the achievable data rate is approximated as \cite{setayesh2020joint}
\begin{equation}\label{eq11}
\mathcal{R}_{u(s_j,i)} = \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
\end{equation}
where
\begin{equation}
\mathcal{R}_{r,u(s_j,i)} = \mathcal{{R}}_{r,u(s_j,i)}^{k}{e}_{u(s_j,i)}^{k},
\end{equation}
is the achievable data rate of RU $r$ to UE $i$ in slice $s_1$, which depends on the achievable data rate per PRB, i.e.,
\begin{equation}
\mathcal{{R}}_{r,u(s_j,i)}^{k} = B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},
\end{equation}
%\begin{subequations}\label{eq11}
%\begin{alignat}{4}
%\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
%\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
%\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)},
%\end{alignat}
%\end{subequations}
where %$j \in \{2,3\}$. Also we have $ \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}},$.
%{\color{red} check paranthesis. }
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}}.
\end{equation}
%{\color{red} what is transmission probability? }
Here, $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of the Q function,
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$ and PRB $k$, while
$N_{u(s_j,i)}^{k}$ represents the corresponding transmit blocklength.
$\mathcal{R}_{r,u(s_j,i)}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

\begin{figure*}[!htb]
	\centerline{%
		\begin{tabular}{c@{}c@{}c}			
			\includegraphics[scale = 0.41]{fig/priorityLastn.eps} &
			\includegraphics[scale = 0.41]{fig/itern.eps} &
			\includegraphics[scale = 0.41]{fig/iterD.eps} \\
			\scriptsize Fig. 9~~Throughput of eMBB services vs. priority of the first one  & \scriptsize Fig. 10~~Aggregate throughput vs. number of iterations  & \scriptsize Fig. 11~~Mean Delay time vs. number of iterations 
	\end{tabular}}
	%\caption{Global caption.}
	\label{label}
\end{figure*}

@@

\textcolor{MidnightBlue}{In Fig. 11, the mean total delay of URLLC service is indicated according to the number of iterations of the
proposed algorithm (IABV) for different numbers of UEs for one URLLC service. This figure shows that the algorithm converged to the fixed value after four iterations.}
